B\'{e}zier $\bar{B}$ projection

### 2018-01-24 projection1120.tex
Update introduction and conclusion.

@@

Following the same pattern as the non-symmetric \Bezier $\bar{B}$ method for the Timoshenko beam problem, we keep the discretization of $\mathbf{u}$ and $\mathbf{w}$ untouched, while using lower order spline basis functions and corresponding dual basis functions for the discretization of pressure $p$ and its variation $\delta{p}$, respectively. The discretized stiffness matrix in mixed form can be written as
\begin{equation}
    \mathbf{K}_{mix}=
    \begin{bmatrix}
        \mathbf{K}^{dev} & -\mathbf{P}^{T}\\
        -\hat{\mathbf{P}} & -\dfrac{1}{(\lambda+2\mu/3)}\mathbf{I}
    \end{bmatrix},
\end{equation}
\added{where}
\begin{equation}
    \mathbf{P}=\A_e\mathbf{P}_e^{vol},
\end{equation}
with
\begin{equation}
    \mathbf{P}_e^{vol}=\bar{\mathbf{C}}^e\langle{\bar{\mathbf{B}}_e^T,\mathbf{B}^{vol}_e}\rangle(\mathbf{C}^e)^T.
\end{equation}
By eliminating the pressure control points, we obtain the pure displacement formulation as
\begin{equation}
	\mathbf{K} = \mathbf{K}^{dev} + \bar{\mathbf{K}}^{vol}_{NS},
\end{equation}
where
\begin{equation}
    \bar{\mathbf{K}}^{vol}_{NS}=(\lambda+2\mu/3){\mathbf{P}}^T\hat{\mathbf{P}}.
\end{equation}

@@

We have presented the B\'{e}zier $\bar{B}$ method as an approach to overcome locking phenomena in structural mechanics applications of isogeometric analysis. The approach utilizes B\'ezier extraction and projection which makes it simple to implement in an existing finite element framework and makes it applicable to any spline representation which can be written in \Bezier form. In contrast to global $\bar{B}$ methods, which produce dense stiffness matrices, the B\'ezier $\bar{B}$ approach results in a sparse stiffness matrix while still benefiting from higher-order convergence rates.

We have demonstrated the performance of the approach in the context of shear deformable beams (to alleviate transverse shear locking) and nearly incompressible elasticity problems (to alleviate volumetric locking). The proposed method reduces locking errors and achieves (nearly) optimal convergence rates. The cases where optimal rates were not achieved warrant further study.
\bibliographystyle{elsarticle-num}
\bibliography{bibliography}
\end{document}

>>>>

\added{In this paper we introduce two methods that employ \Bezier projection to increase the sparsity of the stiffness matrix that results form $\bar{B}$ methods, which typically lead to a dense system. We call these methods the symmetric and non-symmetric \Bezier $\bar{B}$ projection methods based on the resulting symmetry of the stiffness method. We show that both methods result in a sparse stiffness matrix, reduce locking, and result in optimal (non-symmetric method) or near optimal (symmetric method) convergence rates.  We also perform an inf-sup analysis to help provide further insight into the behavior and quality of these methods.}

@@

Following the same pattern as the non-symmetric \Bezier $\bar{B}$ method for the Timoshenko beam problem, we keep the discretization of $\mathbf{u}$ and $\mathbf{w}$ untouched, while using lower order spline basis functions and corresponding dual basis functions for the discretization of pressure $p$ and its variation $\delta{p}$, respectively. The discretized stiffness matrix in mixed form can be written as
\begin{equation}
    \mathbf{K}_{mix}=
    \begin{bmatrix}
        \mathbf{K}^{dev} & -\mathbf{P}^{T}\\
        -\hat{\mathbf{P}} & -\dfrac{1}{(\lambda+2\mu/3)}\mathbf{I}
    \end{bmatrix},
\end{equation}
\added{where}
\begin{equation}
    \mathbf{P}=\A_e\mathbf{P}_e^{vol},
\end{equation}
with
\begin{equation}
    \mathbf{P}_e^{vol}=\bar{\mathbf{C}}^e\langle{\bar{\mathbf{B}}_e^T,\mathbf{B}^{vol}_e}\rangle(\mathbf{C}^e)^T.
\end{equation}
By eliminating the pressure control points, we obtain the pure displacement formulation as
\begin{equation}
	\mathbf{K} = \mathbf{K}^{dev} + \bar{\mathbf{K}}^{vol}_{NS},
\end{equation}
where
\begin{equation}
    \bar{\mathbf{K}}^{vol}_{NS}=(\lambda+2\mu/3){\mathbf{P}}^T\hat{\mathbf{P}}.
\end{equation}
We note, that in contrast to the symmetric \Bezier $\bar{B}$ method, the assembly of the stiffness matrix in this case can be performed in the standard way with no need for global matrix operations.

@@

We have presented two B\'{e}zier $\bar{B}$ projection methods, which we have called symmetric and non-symmetric \Bezier $\bar{B}$ projection, as an approach to overcome locking phenomena in structural mechanics applications of isogeometric analysis while maintaining sparsity of the resulting linear system. The methods utilize B\'ezier extraction and projection, which makes it simple to implement them in an existing finite element framework and makes it applicable to any spline representation which can be written in \Bezier form. In contrast to global $\bar{B}$ methods, which produce dense stiffness matrices, the B\'ezier $\bar{B}$ approach results in a sparse stiffness matrix while still benefiting from higher-order convergence rates. \added{We have made the connection between the non-symmetric method and mixed formulations and shown that although this method does not strictly satisfy the inf-sup condition it reduces constraints sufficiently to provide optimal convergence rates for the problems studied here.}

We have demonstrated the performance of the approach in the context of shear deformable beams (to alleviate transverse shear locking) and nearly incompressible elasticity problems (to alleviate volumetric locking). The proposed method reduces locking errors and achieves (nearly) optimal convergence rates \added{ for the symmetric method and optimal rates for the non-symmetric method}. The cases where optimal rates were not achieved \added{when using the the symmetric formulation are a symptom of the fact that the symmetric formulation has may not satisfy the inf-sup condition}.

\added{These two methods provide a choice between a formulation that results in a symmetric stiffness matrix but requires matrix operations at the global level and potentially less accuracy and a formulation that results in a non-symmetric stiffness matrix that can be assembled in the standard element routine approach and achieves optimal convergence rates. The trade offs are between higher costs in assembly for the symmetric formulation versus potentially higher costs in solving a non-symmetric system for the non-symmetric formulation. In either case, however, the cost is less than using the standard $\bar{B}$ formulation.}
\bibliographystyle{elsarticle-num}
\bibliography{bibliography}
\end{document}
